### 2022-11-20 dissertation/chapters/08-results.tex
🚧 (results): Replay

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{replay window size} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. As a reminder, five different replay window sizes are considered. These include replay window sizes of 1, 5, 10, 15, and 20.

Table \ref{tab:results:replay:metrics} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations. Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and all training epochs.

@@

Table \ref{tab:results:replay:metrics} shows that there is no clear best performing replay window size configuration of the \acs{BHH} for all datasets. A replay window size of 1 is best for the air quality, car, fish toxity and forest fires datasets. A replay window size of 5 is best for the abalone, adult, bike and wine quality datasets. A replay window size of 10 is best for the bank, diabetic, housing, parkinsons and student performance datasets. A replay window size of 15 is best for the iris and mushroom datasets. Finally, the largest replay window size of 20 did not provide the best outcome for any dataset, but provided results very close to that of the other configurations. From these observations it can be concluded that the replay window size is problem specific. This means that some problem sets require a shorter replay window size, while others require a larger replay window size.

Furthermore, it can be concluded that some problem sets require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.

@@

Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs.

@@

Figure~\ref{fig:results:replay:descriptive:cd} shows no statistically significant difference in results for the various replay window size configurations as it relates to all datasets.

Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group. As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for other datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
		\caption{Train log accuracy}
		\label{fig:results:replay:figures:accuracy:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
		\caption{Test log accuracy}
		\label{fig:results:replay:figures:accuracy:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:diabetic}
\end{figure}

Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group. As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for other regression datasets are left out for brevity.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:fish_toxicity}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:fish_toxicity}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:fish_toxicity}
\end{figure}

>>>>

This section provides the empirical results for the experimental group that compares the performance of different variants of the \acs{BHH} as it relates to the \textit{replay window size} hyper-parameter. Brief discussions follow and illustrations are provided for visual aid. As a reminder, five different replay window sizes are considered. These include replay window sizes of 1, 5, 10, 15, and 20. Experiments are denoted as such.

As before, Table~\ref{tab:results:replay:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the replay window size variants of the \acs{BHH} that was implemented. The test loss is measured at the last epoch for each dataset, over all independent runs.
	\caption{Empirical results showing average test loss and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and is measured at the last epoch.}

Table \ref{tab:results:replay:metrics:rank} provides the ranked performance, per dataset, for each of the \acs{BHH} replay window size configurations. Similar to before, the performance rank is calculated as the average rank produced by the replay window size configurations, for all datasets, over all independent runs and all training epochs. The overall normalised average rank is provided at the end of the table.

@@

Tables \ref{tab:results:replay:metrics:loss} and \ref{tab:results:replay:metrics:rank} shows that there is no clear overall best performing replay window size configuration of the \acs{BHH}, for all datasets. In some cases, a replay window size of one yielded the best results. A replay window of one simply considers the last step in the training process. This means that memory of past performance actually had a negative impact on the training process in those particular cases. It should also be observed that the largest replay window size yielded the worst performance overall and also for the most datasets. This suggests that \index{heuristic}heuristic selection is more likely to benefit from short, recent observations in the training process. From these observations it can be concluded that past performances of the \index{heuristic}heuristics are not always beneficial to the training process, and that the replay window size is problem specific. Furthermore, it can be concluded that some problems require more exploration of the \index{heuristic}heuristic space, while other problem sets require more exploitation of low-level \index{heuristic}heuristics.

@@

Figure~\ref{fig:results:replay:descriptive:cd} provides an illustration of the overall critical difference plots for ranked performance for each replay window size configuration as it relates to all datasets, across all independent runs and epochs.

@@

Figure~\ref{fig:results:replay:descriptive:cd} shows no overall statistically significant difference in results for the various replay window size configurations as it relates to all datasets.

Similar to before, Figure~\ref{fig:results:replay:figures:diabetic} provides the train and test, loss and accuracy plots for an example classification dataset (diabetic) as it relates to the replay window size experimental group. As before, the illustrations are provided in log scale and illustrations of the train and test loss and accuracy plots for the other classification datasets are left out for brevity as they yield similar illustrations.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/diabetic.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/diabetic.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/accuracy/diabetic.pdf}
		\caption{Train log accuracy}
		\label{fig:results:replay:figures:accuracy:train:diabetic}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/accuracy/diabetic.pdf}
		\caption{Test log accuracy}
		\label{fig:results:replay:figures:accuracy:test:diabetic}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the diabetic dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:diabetic}
\end{figure}

Figure~\ref{fig:results:replay:figures:fish_toxicity} provides the train and test loss plots for an example regression dataset (fish toxicity) as it relates to the replay window size experimental group. As before, the illustrations are provided in log scale and illustrations of the train and test loss plots for the other regression datasets are left out for brevity.

\begin{figure}[htbp]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/train/loss/fish_toxicity.pdf}
		\caption{Train log loss}
		\label{fig:results:replay:figures:loss:train:fish_toxicity}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{bhh_replay/figures/test/loss/fish_toxicity.pdf}
		\caption{Test log loss}
		\label{fig:results:replay:figures:loss:test:fish_toxicity}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test, loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} with different configurations of the replay window size hyper-parameter on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:replay:figures:fish_toxicity}
\end{figure}

The divergence that can be seen in Figure~\ref{fig:results:replay:figures:loss:train:diabetic} and \ref{fig:results:replay:figures:loss:test:diabetic} is explained in previous sections and is simply a result of the \acs{BHH} considering new \index{heuristic}heuristics that yield sub-optimal results, when an optimal solution has already been found. As mentioned before, an early stopping strategy as well as a move-acceptance strategy can be incorporated to avoid this effect.
